Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-08-19 tex/A.tex
Add explanation about safeguard chains in CH1
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Update intro and abstract
Several concepts have been explained more accurately now.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\title{Argennon: A Scalable Cloud Based Smart Contract Platform}
\author{aybehrouz}
\date{January 2021}

@@

        The Argennon cloud is trustless and publicly verifiable. Computational Integrity (CI) is
        achieved by using succinct argument of knowledge systems (STARK/SNARK)
        and data integrity is guaranteed by cryptographic accumulators. At the same time, a smart
        clustering algorithm keeps the bandwidth usage and the overhead of cryptography manageable
        for validators.

        The Argennon protocol strongly incentivizes the formation of a permission-less network of Publicly Verifiable
        Cloud (PVC) servers. A PVC server in Argennon, is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions.

        These properties make it possible for Argennon to achieve very high transaction throughput while requiring no trust
        in central parties.  
    \end{abstract}
    \tableofcontents

>>>>

\title{Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems}
\author{aybehrouz}
\date{January 2021}

@@

        The Argennon cloud is trustless and publicly verifiable. Computational Integrity (CI) is
        achieved by using succinct argument of knowledge systems (STARK/SNARK)
        and data integrity is guaranteed by cryptographic accumulators.

        The Argennon protocol strongly incentivizes the formation of a permission-less network of Publicly Verifiable
        Cloud (PVC) servers. A PVC server in Argennon, is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions.
    \end{abstract}
    \tableofcontents

### 2022-08-19 tex/sections/intro.tex
Update intro and abstract
Several concepts have been explained more accurately now.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block is required to get approved by its corresponding validator committee.
Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system.
Every committee of validators has an index between $0$ and $m - 1$, and is responsible for validating block number $n$,
if $n$ modulo $m$ equals the committee index. A block is approved if it takes approval votes from at least $2/3$ of
the total stake of its validator committee.

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the committee of validators. A block is considered final after its \textbf{next} block gets \textbf{both} of
its certificates. The Argennon protocol ensures that as long as more than half of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

@@

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the final ledger state of the block (i.e.\ the ledger state after executing all transactions of the block). The CI
set defines how the final state of the block can be reached from
the state of its previous block via a set of intermediate states.
Each individual CI statement defines an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the state before and after executing those requests:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

@@

The Argennon protocol strongly incentivizes the formation of a \textbf{permission-less} network of Publicly Verifiable
Cloud (PVC) servers. To do so, the Argennon protocol conducts repetitive automatic lotteries between PVC servers.
A PVC server can increase its chance of winning by (i) generating proofs for more CI statements, (ii) providing the
state data to more validators and, (iii) storing all parts of the state instead of more frequently used parts.

>>>>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block gets certified by all members of the delegates committee and after that it required to get approved
by its corresponding validator committee.

Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the Argennon network.
Every committee of validators has an index between $0$ and $m - 1$, and is responsible for validating block number $n$,
if $n$ modulo $m$ equals the committee index. A block is approved if it takes approval votes from at least $2/3$ of
the total stake of its validator committee.

In case the main committee fails to generate new blocks or behaves maliciously, a special Recovery Protocol is
initiated by validators.
This recovery protocol can recover the functionality
of the Argennon blockchain as long as more than $2/3$ of the total stake of the system is controlled by honest users
and any network partition resolves after a finite amount of time. The Recovery Protocol uses two main emergency
procedures to recover the functionality of the Argennon blockchain: \emph{emergency forking} and \emph{emergency
agreement} protocol.

In Argennon, a block is considered final after its \textbf{next} block gets certified by \textbf{both} delegates and
validator committees.
The Argennon protocol ensures that as long as more than half of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

@@

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the final ledger state of the block (i.e.\ the ledger state after executing all transactions of the block). The CI
set defines how the final state of the block can be reached from
the state of its previous block via a set of intermediate state transitions. Each individual CI statement defines
an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the state before and after executing those requests.

More formally, each CI statement has the form $\tau(\mathbb{S}, \mathbb{R}, \hat{\mathbb{S}})$, and states that
$\hat{\mathbb{S}}$ is the commitment of the next state after executing an ordered list of external requests with commitment
$\mathbb{R}$ on a state with commitment $\mathbb{S}$.
Commitments to states are produced by a cryptographic accumulator.
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud and efficiently validate a block.

@@

The Argennon protocol strongly incentivizes the formation of a \textbf{permission-less} network of Publicly Verifiable
Cloud (PVC) servers. To do so, the Argennon protocol conducts repetitive automatic lotteries between PVC servers.
A PVC server can increase its chance of winning by (i) generating proofs for more CI statements, (ii) storing all
parts of the ledger state and providing \emph{proofs of storage}.
